% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage[utf8]{inputenc}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{\textbf{Max}imiliano Lopes \textbf{Santiago}}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{git@github.com:corlen/CV.git}

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  %pdfkeywords = {IT, programming, software development},
  pdftitle = {\name: Curriculum Vitae - Maximiliano Santiago},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

\begin{document}

\begin{flushright}

{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Cellphone: & +55 85 8884-9319 \\
    Phone: &  +55 85 3262-0205 \\
    Email: & \href{mailto:maximiliano.santiago@gmail.com}{\tt maximiliano.santiago@gmail.com} \\
    Skype: & \tt maximiliano.santiago \\
    Linkedin: & \href{http://www.linkedin.com/pub/maximiliano-santiago/a/145/b2a}{\tt Maximiliano Santiago} \\
	  Github: & \href{http://github.com/corlen}{\tt http://github.com/corlen} \\
  \end{tabular}
\end{minipage}
\end{flushright}
\section*{Experience Overview}

Maximiliano Santiago has a Degree in Computer Science. He is a professional computing
specialist with more than 13 years experience in advanced software analysis and design,
having gathered knowledge on various platforms and programming languages. Among these
are: Java, Ruby, PHP and ASP 3.0.
He has advanced English and basic French language skills.

\section*{Education}

\begin{itemize}
  \item Student of Economics, Federal University of Ceará, 2013 - Now
  \item B.S. Computer Science, Universidade de Fortaleza, 2007.
\end{itemize}

\section*{Employment and Experience}

\subsection*{M2M IT Solutions(Sep/2011 - Now)}
\begin{itemize}
\item Desenvolvimento de aplicações para gestão de sistemas de transporte público.
\item Clients: Public Transportation Sector
\item Technologies envolved: Java platform, Ruby platform, GXT, GWT, Hibernate, Spring and Rails frameworks, PostgreSQL development and JQuery.
\end{itemize}
\subsection*{CPQi IT Offshore Solutions(Aug/2010 - Aug/2011)}
\begin{itemize}
\item Development of a completely new financial system using the Calypso platform, interfacing with existing mainframe systems.
\item Development of customization products using the Reuters Kondor+ platform and interfacing with existing mainframe systems.
\item Defining scope and solve some technical issues for Calypso platform for BCP(Banco de Crédito del Peru).
\item Clients: Rabobank and HSBC
\item Technologies envolved: Java platform, Oracle platform and Calypso Framework. Sybase and Kondor+ platform.
\item Segment: Financial Banks
\end{itemize}
\subsection*{Instituto Atlântico(Aug/2008 - Jul/2010)}
\begin{itemize}
\item Development of two products for Sony Ericsson cellphones, a level indicator and a chat client
\item Technologies envolved: J2ME and frameworks from Sony Ericsson
\item Clients: Sony Ericsson
\item Segment: Mobile Applications
\end{itemize}
\subsection*{Stefanini IT Solutions(Jan/2008 - Jul/2008)}
\begin{itemize}
\item Development and maintenance in SABIUS system, a manager software of insurance web based
\item Technologies envolved: J2EE Frameworks, IReport and Jasper tools
\item Clients: UNIMED - Health insurance company
\item Segment: Health Insurance
\end{itemize}
\subsection*{CEGÁS (Energy company of Ceará)(Jan/2006 - Dec/2007)}
\begin{itemize}
\item Design, development and maintenance of a complete intranet solution with Java Web.
\item Integration with ERP Logix.
\item Technologies envolved: PHP, Java with Struts Framework and IReport tools.
\item Client: CEGÁS
\item Segment: Energy
\end{itemize}

\section*{Main Skills}
\begin{itemize}
  \item Java Technologies (Java Platform including J2SE, J2EE and J2ME) and support technologies such as GXT, GWT, Ant, Hibernate, Spring, Struts and Android framework. 
  \item SGBDs: Oracle, Sybase, MySQL, SQL Server and PostgreSQL.
  \item Front-end tools: JQuery e Knockout  
  \item Unix (Linux and MacOS X)
  \item UML Modeling and Database Modeling
  \item Programming Languages: Java, Ruby and PHP
  \item Development methodologies such as RUP and agile such as SCRUM
  \item Microsoft Technologies (ASP 3.0, API Win32)
  \item Tools: Rational Unified Modeler, Enterprise Architect, Eclipse, Aptana, debuggers and profilers (language and platform specific) and unit tests.
  \item Report Tools such as iReport and Jasper Reports
\end{itemize}

\section*{Certifications}
\begin{itemize}
  \item SCRUM MASTER Certified
\end{itemize}

\section*{International Experience}
\begin{itemize}
  \item Lima (Peru) - 20 days (BCP Project)
\end{itemize}

\bigskip

\section*{Reference}

\begin{itemize}
\item Calypso Platform- www.calypso.com
\item Kondor+ Platform - www.thomsonreuters.com
\item ERP Logix - www.totvs.com
\end{itemize}

\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
